---
title: "Calculation of climatic indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculation of climatic indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The aim of this vignette is to show the calculation of all statistical indicators
only related to meteorological data (indicator evolving flow are excluded).

```{r setup}
library(EXstat.CARD)
library(airGRdatasets)
library(dplyr)
```

## Presentation of the dataset

The package **airGRdatasets** provides time series for gauging stations located
on Metropolitan French territory.

The river basins present in this package are:

```{r}
# Get all data sets in the package
station_ids <- ls("package:airGRdatasets")

# Create a table with meta data of each gauging station
station_metadata <- dplyr::bind_rows(
  lapply(station_ids,
  function(id){
    data <- base::get(id)
    data.frame(CodeH3 = data$Meta$Code$H3,
               Name = data$Meta$Name,
               Latitude = data$Meta$Coor$Y,
               Longitude = data$Meta$Coor$X,
               start = first(data$TS$Date),
               end = last(data$TS$Date))
  })
)
knitr::kable(station_metadata)
```

We select randomly 3 stations for this vignette.

```{r}
sel_ids <- sample(station_ids, size = 3)
sel_ids
```

And we concat and format the data of these three stations:

```{r}
df_ts <- dplyr::bind_rows(
  lapply(sel_ids,
  function(id){
    df <- base::get(id)$TS
    df$id <- id
    return(df)
  })
)
df_ts$Date <- as.Date(df_ts$Date) # Convert to date format
str(df_ts)
```

## Statistical indicators for temperatures

We list all available indicators for temperature data.

We use the function `CARD_list_all()` to get the complete list of available
indicators.

```{r}
metaEX_all = CARD_list_all()
str(metaEX_all)
```

On which we can filter criteria on temperatures:

```{r}
metaEX_temp <- metaEX_all %>%
  filter(grepl("Temperature", topic_en),
         !grepl("Sensitivity_to_Climate_Variability", script_path))
knitr::kable(metaEX_temp %>% select("variable_en", "name_en"))
```

Then, we format the data for the function `CARD_extraction()`.

```{r}
df_temp <- df_ts %>%
  select("Date", "id", "Temp") %>%
  rename(T = "Temp")
str(df_temp)
```

And run the extraction of indicators!

```{r}
res_temp <- CARD_extraction(
  df_temp,
  CARD_name = metaEX_temp$variable_en
)
str(res_temp)
```

## Statistical indicators for potential evapotranspiration

We select all criteria on evaporation except the one evolving flow.

```{r}
metaEX_evap <- metaEX_all %>%
  filter(grepl("Evapotranspiration", topic_en),
         !grepl("Flow", topic_en))
knitr::kable(metaEX_evap %>% select("variable_en", "name_en"))
```

Then, we format the data and run the function `CARD_extraction()`.

```{r}
df_evap <- df_ts %>%
  select("Date", "id", "Evap") %>%
  rename(ETP = "Evap") # R is the precipitation variable in the dataframe
str(df_evap)
res_evap <- CARD_extraction(
  df_evap,
  CARD_name = metaEX_evap$variable_en
)
str(res_evap)
```

## Statistical indicators for precipitations

We select all criteria on precipitations except:

- criteria using flow,
- criteria related to parametrization, sensitivity to climate variability, or ratio
- criteria related to liquid or solid precipitations

```{r}
metaEX_prec <- metaEX_all %>%
  filter(grepl("Precipitation", topic_en),
         !grepl("Flow|Parameterization|Sensitivity to Climate Variability|Ratio", topic_en),
         !grepl("liquid|solid|Annual precipitation", name_en))
knitr::kable(metaEX_prec %>% select("variable_en", "name_en"))
```

Then, we format the data and run the function `CARD_extraction()`.

```{r}
df_prec <- df_ts %>%
  select("Date", "id", "Ptot") %>%
  rename(R = "Ptot") # R is the precipitation variable in the dataframe
str(df_prec)
res_prec <- CARD_extraction(
  df_prec,
  CARD_name = metaEX_prec$variable_en
)
str(res_prec)
```
