---
title: "Calculation of hydrological indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculation of hydrological indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The aim of this vignette is to show the calculation of all statistical indicators
only related to flow data (indicator evolving precipitation and comparison between
observed and simulated flows are excluded).

```{r setup}
library(EXstat.CARD)
library(airGRdatasets)
library(dplyr)
```

# Dataset

We use flow time series of three random gauging stations provided by the package
**airGRdatasets** (See vignette `V01-climatic_indicators` for more details).

```{r}
# Get all data sets in the package
station_ids <- ls("package:airGRdatasets")
# Sample 3 stations
sel_ids <- sample(station_ids, size = 3)
sel_ids
# "Tidy format" the time series
df_ts <- dplyr::bind_rows(
  lapply(sel_ids,
  function(id){
    df <- base::get(id)$TS
    df$id <- id
    return(df)
  })
)
df_ts$Date <- as.Date(df_ts$Date) # Convert to date format
str(df_ts)
```

## Selection of hydrological indicators

We use the function `CARD_list_all()` to get the complete list of available
indicators.

```{r}
metaEX_all = CARD_list_all()
str(metaEX_all)
```

On which we can filter criteria on flows excluding indicators related to:

- performance of hydrological model
- indicators computed for future horizon periods
- sensitivity to climate variability
- indicators invoking the currently bugged function `GeneralMannKendall_WRAP`
- the indicator `med{dtRec}` that is currently crashing

```{r}
metaEX_flow <- metaEX_all %>%
  filter(grepl("Flow", topic_en),
         !grepl("Performance", topic_en),
         !grepl("_H[0-3]*$" , variable_en),
         !grepl("Sensitivity_to_Climate_Variability", script_path),
         # 'GeneralMannKendall_WRAP' is not an exported object from 'namespace:EXstat'
         !grepl("alpha" , variable_en),
         # Error in `dplyr::arrange()`: In argument: `..1 = get(date_col)`
         variable_en != "med{dtRec}")
knitr::kable(metaEX_flow %>% select("variable_en", name_en))
```

Finally, we format the data and run the function `CARD_extraction()`.

```{r}
df_flow <- df_ts %>%
  select("Date", "id", "Qls") %>%
  rename(Q = "Qls") %>%
  mutate(Q = Q / 1000) # Convert to m3/s
str(df_flow)
res_flow <- CARD_extraction(
  df_flow,
  CARD_name = metaEX_flow$variable_en
)
str(res_flow)
```
